% -*- latex -*-


\setDate{November 15, 2006}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetGetStrategyName}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetGetStrategyName} -- retrieve strategy name.}

  \mansection{Synopsis}

  \textC{\#include <GL/ice-t.h>}

  \begin{Table}{3}
    \textC{const GLubyte }\CFunc{icetGetStrategyName}\textC{(}&\textC{void}&\textC{);}
  \end{Table}

  
  \mansection{Description}

  \CFunc{icetGetStrategyName} retrieves a human readable name for the
  current strategy.


  \mansection{Return Value}

  Returns a short, null terminated string identifying the strategy
  currently in effect.  Helpful for printing out debugging or diagnostic
  statements.  If no strategy is set, \textC{NULL} is returned.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Notes}

  The string returned does
  \emph{not}
  contain the identifier used in a C program.  For example, if the current
  strategy is
  \CEnum{ICET\_STRATEGY\_REDUCE}, \CFunc{icetGetStrategyName}
  returns ``Reduce,'' not ``ICET\_STRATEGY\_REDUCE.''


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetStrategy}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
