% -*- latex -*-


\setDate{July 20, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetCopyState}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetCopyState} -- copy state machine of one context to another.}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetCopyState}\textC{(}&\CType{IceTContext}&\CArg{dest}\textC{,} \\
      &\textC{const }\CType{IceTContext}&\CArg{src}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  The \CFunc{icetCopyState} function replaces the state of \CArg{dest} with
  the current state of \CArg{src}.  This function can be used to quickly
  duplicate a context.

  The \CType{IceTCommunicator} object associated with \CArg{dest} is
  \emph{not} changed (nor can it ever be).  Consequently, the following
  state values are not copied either, since they refer to process ids that
  are directly tied to the \CType{IceTCommunicator} object:
  \CEnum{ICET\_RANK}, \CEnum{ICET\_NUM\_PROCESSES},
  \CEnum{ICET\_DATA\_REPLICATION\_GROUP},
  \CEnum{ICET\_DATA\_REPLICATION\_GROUP\_SIZE},
  \CEnum{ICET\_COMPOSITE\_ORDER}, and \CEnum{ICET\_PROCESS\_ORDERS}.
  However, every other state parameter is copied.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  The state is copied blindly.  It is therefore possible to copy states
  that are invalid for a context's communicator.  For example, a display
  rank may not refer to a valid process id.


  \mansection{Notes}

  Behavior is undefined if \CArg{dest} or \CArg{src} has never been created
  or has already been destroyed.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetCreateContext},
  \CFuncSeeAlso{icetGetContext},
  \CFuncSeeAlso{icetSetContext}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
