% -*- latex -*-


\setDate{July 28, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetImageGetColorFormat}{Kenneth Moreland}{\IceT Reference}{\icetImageGetColorFormat, \icetImageGetDepthFormat -- get the format of image buffers}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{5}
    \textC{IceTEnum}&\icetImageGetColorFormat\textC{(}&\textC{const }\CType{IceTImage}&\CArg{image}&\textC{);} \\
    \textC{IceTEnum}&\icetImageGetDepthFormat\textC{(}&\textC{const }\CType{IceTImage}&\CArg{image}&\textC{);}
  \end{Table}

  
  \mansection{Description}

  \icetImageGetColorFormat and \icetImageGetDepthFormat return an entry in
  an enumeration that specifies the data format stored in the given
  \CArg{image}.  This format determines which one of the
  \CFunc{icetImageGetColor} or \CFunc{icetImageGetDepth} functions to use
  and the form of the resulting data.


  \mansection{Return Value}

  \icetImageGetColorFormat returns one of the following values with the
  associated meaning for the format of the stored color data.

  @enum_image_color@

  \icetImageGetDepthFormat returns one of the following values with the
  associated meaning for the format of the stored depth data.

  @enum_image_depth@


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Copyright}
  Copyright \copyright 2010 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetImageGetColor},
  \CFuncSeeAlso{icetImageGetDepth},
  \CFuncSeeAlso{icetSetColorFormat},
  \CFuncSeeAlso{icetSetDepthFormat}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
