% -*- latex -*-


\setDate{September 22, 2014}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetSetColorFormat}{Kenneth Moreland}{\IceT Reference}{\icetSetColorFormat, \icetSetDepthFormat -- specifies the buffer formats for \IceT to use when creating images }

  \label{manpage:icetSetDepthFormat}
  \index{icetSetDepthFormat|(textbf}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\icetSetColorFormat\textC{(}&\textC{IceTEnum}&\CArg{color\_format}\quad\textC{);} \\
    \textC{void }\icetSetDepthFormat\textC{(}&\textC{IceTEnum}&\CArg{depth\_format}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  When \IceT creates image objects, it uses the formats specified by
  \icetSetColorFormat and \icetSetDepthFormat.  These will be the formats
  of images passed to drawing callbacks (specified by
  \CFunc{icetDrawCallback} or \CFunc{icetGLDrawCallback}) and of images
  returned from frame drawing functions (\CFunc{icetDrawFrame} or
  \CFunc{icetGLDrawFrame}). It is also the format expected for image
  buffers passed to \CFunc{icetCompositeImage}.

  The following \CArg{color\_format}s are valid for use in
  \icetSetColorFormat.

  @enum_image_color@

  The following \CArg{depth\_format}s are valid for use in
  \icetSetDepthFormat.

  @enum_image_depth@

  The color and depth formats are stored in the \CEnum{ICET\_COLOR\_FORMAT}
  and \CEnum{ICET\_DEPTH\_FORMAT} state variables, respectively.


  \mansection{Errors}

  \begin{Description}[ICET\_INVALID\_OPERATION]
  \item[\CErrorEnum{ICET\_INVALID\_OPERATION}] \icetSetColorFormat or
    \icetSetDepthFormat was called while \IceT was drawing a frame.  This
    probably means that you called icetSetColorFormat in a drawing
    callback. You cannot do that. Call this function before starting the
    draw operation.
  \item[\CErrorEnum{ICET\_INVALID\_ENUM}]
    The \CArg{color\_format} or \CArg{depth\_format} given is invalid.
  \end{Description}


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Notes}

  Calling either \icetSetColorFormat or \icetSetDepthFormat does \emph{not}
  change the format of any existing images.  It only changes any
  subsequently created images.

  The color format must be set before calling \CFunc{icetDrawFrame},
  \CFunc{icetGLDrawFrame}, or \CFunc{icetCompositeImage}.  Doing otherwise
  would create inconsistencies in the images created and composited
  together.


  \mansection{Copyright}
  Copyright \copyright 2010 Sandia Corporation

  @copyright@

  \mansection{See Also}

  \CFuncSeeAlso{icetImageGetColorFormat},
  \CFuncSeeAlso{icetImageGetDepthFormat}

  \index{icetSetDepthFormat|)textbf}
\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
