% -*- latex -*-


\setDate{July 29, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetDiagnostics}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetDiagnostics} -- change diagnostic reporting level.}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetDiagnostics}\textC{(}&\textC{IceTBitField}&\CArg{mask}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  Sets what diagnostic message are printed to standard output.  The
  messages to be printed out are defined by \CArg{mask}.  \CArg{mask}
  consists of flags that are OR-ed together.  The valid flags are:
  \begin{Description}[xxxxxxxx]
  \item[\CEnum{ICET\_DIAG\_OFF}]
    A zero flag used to indicate that no diagnostic messages are desired.
  \item[\CEnum{ICET\_DIAG\_ERRORS}]
    Print messages associated with anomalous conditions.
  \item[\CEnum{ICET\_DIAG\_WARNINGS}]
    Print messages associated with conditions that are unexpected or may lead
    to errors.  Implicitly turns on \CEnum{ICET\_DIAG\_ERRORS}.
  \item[\CEnum{ICET\_DIAG\_DEBUG}]
    Print frequent messages concerning the status of \IceT.  Implicitly
    turns on \CEnum{ICET\_DIAG\_ERRORS} and \CEnum{ICET\_DIAG\_WARNINGS}.
  \item[\CEnum{ICET\_DIAG\_ROOT\_NODE}]
    Print messages only on the node with a process rank of 0.  This is the
    default if neither \CEnum{ICET\_DIAG\_ROOT\_NODE} nor
    \CEnum{ICET\_DIAG\_ALL\_NODES} is set.
  \item[\CEnum{ICET\_DIAG\_ALL\_NODES}]
    Print messages all every nodes.
  \item[\CEnum{ICET\_DIAG\_FULL}]
    Turn on all diagnostic messages on all nodes.
  \end{Description}

  The default flags are \CEnum{ICET\_DIAG\_ALL\_NODES} $|$
  \CEnum{ICET\_DIAG\_WARNINGS}.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetGetError}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
