% -*- latex -*-


\setDate{November 15, 2006}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetGetError}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetGetError} -- return the last error condition.}

  \mansection{Synopsis}

  \textC{\#include <GL/ice-t.h>}

  \begin{Table}{3}
    \textC{GLenum }\CFunc{icetGetError}\textC{(}&\textC{void}&\textC{);}
  \end{Table}

  
  \mansection{Description}

  Retrieves the first error or warning condition that occurred since the
  last call to \CFunc{icetGetError} or since program startup, whichever
  happened last.

  Once an error condition has been retrieved with \CFunc{icetGetError}, the
  error condition is reset to no error and cannot be retrieved again.


  \mansection{Return Value}

  One of the following flags will be returned:
  \begin{Description}[ICET\_INVALID\_OPERATION]
  \item[\CEnum{ICET\_INVALID\_VALUE}] An inappropriate value has been
    passed to a function.
  \item[\CEnum{ICET\_INVALID\_OPERATION}] An inappropriate function has
    been called.
  \item[\CEnum{ICET\_OUT\_OF\_MEMORY}] \IceT has ran out of memory for
    buffer space.
  \item[\CEnum{ICET\_BAD\_CAST}] A function has been passed a value of the
    wrong type.
  \item[\CEnum{ICET\_INVALID\_ENUM}] A function has been passed an invalid
    constant.
  \item[\CEnum{ICET\_SANITY\_CHECK\_FAIL}] An internal error (or warning)
    has occurred.
  \item[\CEnum{ICET\_NO\_ERROR}] No error has been raised since the last
    call to \CFunc{icetGetError}.
  \end{Description}


  \mansection{Bugs}

  It is not possible to tell if the returned value was caused by an error
  or a warning.


  \mansection{Notes}

  The error value is \emph{not} context dependent.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetDiagnostics}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
