% -*- latex -*-


\setDate{July 20, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetDestroyContext}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetDestroyContext} -- delete a context.}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetDestroyContext}\textC{(}&\CType{IceTContext}&\CArg{context}\quad\textC{;}
  \end{Table}

  
  \mansection{Description}

  Frees the memory required to hold the state of \CArg{context} and removes
  \CArg{context} from existence.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  \CFunc{icetDestroyContext} will happily delete the current context for
  you, but subsequent calls to most other \IceT functions will probably
  result in seg-faults unless you make another context current with
  \CFunc{icetCreateContext} or \CFunc{icetSetContext}.  The most notable
  execptions are the functions with names matching \textCF{icet*Context},
  which will work correctly without a proper current context.


  \mansection{Notes}

  Behavior is undefined if \CArg{context} has never been created or has
  already been destroyed.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetCreateContext}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
