% -*- latex -*-


\setDate{August  9, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetDataReplicationGroupColor}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetDataReplicationGroupColor} -- define data replication.}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetDataReplicationGroupColor}\textC{(}&\textC{IceTInt}&\CArg{color}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  \IceT has the ability to take advantage of geometric data that is
  replicated among processes.  If a group of processes share the same
  geometry data, then \IceT will split the region of the display that the
  data projects onto among the processes, thereby reducing the total amount
  of image composition work that needs to be done.

  Despite the name of the function, \CFunc{icetDataReplicationGroupColor}
  has nothing to do the color of the data being replicated.  Instead,
  \CArg{color} is used to mark the local process as part of a given group.
  When \CFunc{icetDataReplicationGroupColor} is called, it finds all other
  processes that have the same color and builds a group based on this
  information.

  \CFunc{icetDataReplicationGroupColor} must be called on every processes
  before the function will return.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  \IceT assumes that \CFunc{icetDataReplicationGroup} is called with the
  exact same parameters on all processes belonging to a given group.
  Likewise, \IceT also assumes that all processes have called
  \CFunc{icetBoundingVertices} or \CFunc{icetBoundingBox} with the exact
  same parameters on all processes belonging to a given group.  These
  requirements are not strictly enforced, but failing to do so may cause
  some of the geometry to not be rendered.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  @copyright@

  \mansection{See Also}

  \CFuncSeeAlso{icetDataReplicationGroup},
  \CFuncSeeAlso{icetDrawFunc},
  \CFuncSeeAlso{icetBoundingVertices},
  \CFuncSeeAlso{icetBoundingBox}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
