% -*- latex -*-


\setDate{December  1, 2006}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetWallTime}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetWallTime} -- timer function}

  \mansection{Synopsis}

  \textC{\#include <GL/ice-t.h>}

  \begin{Table}{3}
    \textC{double }\CFunc{icetWallTime}\textC{(}&\textC{void}&\textC{)}
  \end{Table}

  
  \mansection{Description}

  Retrieves the current time, in seconds.  The returned values of
  \CFunc{icetWallTime} are only valid in relation to each other.  That is,
  the time may or may not have anything to do with the current date or
  time.  However, the difference of values between two calls to
  \CFunc{icetWallTime} is the elapsed time in seconds between the two
  calls.  Thus, \CFunc{icetWallTime} is handy for determining the running
  time of various subprocesses.  \CFunc{icetWallTime} is used internally
  for determining the values for the state variables
  \CEnum{ICET\_BUFFER\_READ\_TIME}, \CEnum{ICET\_BUFFER\_WRITE\_TIME},
  \CEnum{ICET\_COMPARE\_TIME}, \CEnum{ICET\_COMPOSITE\_TIME},
  \CEnum{ICET\_COMPRESS\_TIME}, \CEnum{ICET\_RENDER\_TIME}, and
  \CEnum{ICET\_TOTAL\_DRAW\_TIME}.


  \mansection{Return Value}

  The current time, in seconds.


  \mansection{Errors}

  \begin{Description}[ICET\_INVALID\_OPERATION]
  \item[\CErrorEnum{ICET\_INVALID\_VALUE}]
    You've screwed up something a little bit.
  \item[\CErrorEnum{ICET\_INVALID\_OPERATION}]
    You've screwed something up a lot.
  \item[\CErrorEnum{ICET\_OUT\_OF\_MEMORY}]
    You need a better computer to do what you want to do.
  \item[\CErrorEnum{ICET\_BAD\_CAST}]
    The argument is of the wrong format.
  \item[\CErrorEnum{ICET\_INVALID\_ENUM}]
    One of us does not know what he is talking about.
  \item[\CErrorEnum{ICET\_SANITY\_CHECK\_FAIL}]
    I've screwed something up a lot.
  \end{Description}


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Notes}

  This man page should never be installed.  It should just be used to help
  make other man pages.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetGet}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
