% -*- latex -*-


\setDate{July 20, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetBoundingBox}{Kenneth Moreland}{\IceT Reference}{\icetBoundingBoxd, \icetBoundingBoxf\ -- set bounds of geometry}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\icetBoundingBoxd\textC{(}&\textC{IceTDouble}&\CArg{x\_min}\textC{,} \\
      &\textC{IceTDouble}&\CArg{x\_max}\textC{,} \\
      &\textC{IceTDouble}&\CArg{y\_min}\textC{,} \\
      &\textC{IceTDouble}&\CArg{y\_max}\textC{,} \\
      &\textC{IceTDouble}&\CArg{z\_min}\textC{,} \\
      &\textC{IceTDouble}&\CArg{z\_max}\quad\textC{);}
  \end{Table}

  \begin{Table}{3}
    \textC{void }\icetBoundingBoxf\textC{(}&\textC{IceTFloat}&\CArg{x\_min}\textC{,} \\
      &\textC{IceTFloat}&\CArg{x\_max}\textC{,} \\
      &\textC{IceTFloat}&\CArg{y\_min}\textC{,} \\
      &\textC{IceTFloat}&\CArg{y\_max}\textC{,} \\
      &\textC{IceTFloat}&\CArg{z\_min}\textC{,} \\
      &\textC{IceTFloat}&\CArg{z\_max}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  Establishes the bounds of the geometry as contained in an axis-aligned
  box with the given extents.

  \icetBoundingBoxd\ and \icetBoundingBoxf\ are really just convience
  functions.  They create an array of the 8 corner vertices and set the
  bounding vertices appropriately.  See \CFunc{icetBoundingVertices} for
  more information.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetBoundingVertices}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
