% -*- latex -*-


\setDate{July 20, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetBoundingVertices}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetBoundingVertices} -- set bounds of geometry.}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetBoundingVertices}\textC{(}&\textC{IceTInt}&\CArg{size}\textC{,} \\
      &\textC{IceTEnum}&\CArg{type}\textC{,} \\
      &\textC{IceTSizeType}&\CArg{stride}\textC{,} \\
      &\textC{IceTSizeType}&\CArg{count}\textC{,} \\
      &\textC{const IceTVoid *}&\CArg{pointer}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  \CFunc{icetBoundingVertices} is used to tell \IceT what the bounds of
  the geometry drawn by the callback registered with \CFunc{icetDrawFunc}
  are.  The bounds are assumed to be the convex hull of the vertices given.
  The user should take care to make sure that the drawn geometry actually
  does fit within the convex hull, or the data may be culled in unexpected
  ways.  \IceT runs most efficiently when the bounds given are tight
  (match the actual volume of the data well) and when the number of
  vertices given is minimal.

  The \CArg{size} parameter specifies the number of coordinates given for
  each vertex.  Coordinates are given in X-Y-Z-W order.  Any Y or Z
  coordinate not given (because \CArg{size} is less than 3) is assumed to
  be $0.0$, and any W coordinate not given (because \CArg{size} is less
  than 4) is assumed to be $1.0$.

  The \CArg{type} parameter specifies in what data type the coordinates are
  given.  Valid \CArg{type}s are \CEnum{ICET\_SHORT}, \CEnum{ICET\_INT},
  \CEnum{ICET\_FLOAT}, and \CEnum{ICET\_DOUBLE}, which correspond to types
  \textC{IceTShort}, \textC{IceTInt}, \textC{IceTFloat}, and
  \textC{IceTDouble}, respectively.

  The \CArg{stride} parameter specifies the offset between consecutive
  vertices in bytes.  If \CArg{stride} is $0$, the array is assumed to be
  tightly packed.

  The \CArg{count} parameter specifies the number of vertices to set.

  The \CArg{pointer} parameter is an array of vertices with the first
  vertex starting at the first byte.

  If data replication is being used, each process in a data replication
  group should register the same bounding vertices that encompass the
  entire geometry.  By default there is no data replication, so unless you
  call \CFunc{icetDataReplicationGroup}, all process can have their own
  bounds.


  \mansection{Errors}

  \begin{Description}[ICET\_INVALID\_OPERATION]
  \item[\CErrorEnum{ICET\_INVALID\_ENUM}]
    Raised if \CArg{type} is not one of \CEnum{ICET\_SHORT},
    \CEnum{ICET\_INT}, \CEnum{ICET\_FLOAT}, or \CEnum{ICET\_DOUBLE}.
  \end{Description}


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetDrawFunc}, \CFuncSeeAlso{icetBoundingBox},
  \CFuncSeeAlso{icetDataReplicationGroup}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
