% -*- latex -*-


\setDate{August  9, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetSingleImageStrategy}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetSingleImageStrategy} -- set the sub-strategy used to composite the image for a single tile.}

  \mansection{Synopsis}

  \textC{\#include <IceT.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetSingleImageStrategy}\textC{(}&\textC{IceTEnum}&\CArg{strategy}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  The main \IceT algorithms are specially designed to composite data
  defined on multiple tiles.  Some of these algorithms, namely
  \CEnum{ICET\_STRATEGY\_REDUCE} and \CEnum{ICET\_STRATEGY\_SEQUENTIAL},
  operate at least in part by compositing single images together.  \IceT
  also comes with multiple separate strategies for performing this single
  image compositing, and this can be selected with the
  \CFunc{icetSingleImageStrategy} function.

  A single image strategy is chosen from one of the following provided
  enumerated values:

  @enum_single_image_strategy@

  By default \IceT sets the single image strategy to
  \CEnum{ICET\_SINGLE\_IMAGE\_STRATEGY\_AUTOMATIC} when a context is
  created.  This is the single image strategy that will be used if no other
  is selected.

  \mansection{Errors}

  \begin{Description}[ICET\_INVALID\_OPERATION]
  \item[\CErrorEnum{ICET\_INVALID\_ENUM}]
    The \CArg{strategy} argument does not represent a valid single image
    strategy.
  \end{Description}


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Copyright}
  Copyright \copyright 2010 Sandia Corporation

  @copyright@

  \mansection{See Also}

  \CFuncSeeAlso{icetDrawFrame},
  \CFuncSeeAlso{icetGetStrategyName}
  \CFuncSeeAlso{icetSingleImageStrategy}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
