% -*- latex -*-


\setDate{December  1, 2006}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetResetTiles}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetResetTiles} -- clears out all tile definitions.}

  \mansection{Synopsis}

  \textC{\#include <GL/ice-t.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetResetTiles}\textC{(}&\textC{void}&\textC{)}
  \end{Table}

  
  \mansection{Description}

  \IceT defines its display as a set of tiles.  \CFunc{icetResetTiles} will
  empty this set.  The set of tiles is filled again with calls to
  \CFunc{icetAddTile}.

  As a side effect, \CFunc{icetResetTiles} will also zero out the
  renderable window size.  The size will be reset with calls to
  \CFunc{icetAddTile}.


  \mansection{Errors}

  None.


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  None known.


  \mansection{Notes}

  As a rule, a call to \CFunc{icetResetTiles} should always be followed
  with one or more calls to \CFunc{icetAddTile}.  \CFunc{icetDrawFrame}
  will not work properly if no tiles are in existence.


  \mansection{Copyright}
  Copyright \copyright 2003 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetAddTile}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
