% -*- latex -*-


\setDate{July 29, 2010}
% The following must all be on one line for latex2man to work.
\begin{Name}{3}{icetGLSetReadBuffer}{Kenneth Moreland}{\IceT Reference}{\CFunc{icetGLSetReadBuffer} -- set \OpenGL buffer for images}

  \mansection{Synopsis}

  \textC{\#include <IceTGL.h>}

  \begin{Table}{3}
    \textC{void }\CFunc{icetGLSetReadBuffer}\textC{(}&\textC{GLenum}&\CArg{mode}\quad\textC{);}
  \end{Table}

  
  \mansection{Description}

  Set the \OpenGL buffer from which to read images to composite.  After the
  draw callback (specified by \CFunc{icetGLDrawCallback}) returns, \IceT
  grabs the rendered image from the \OpenGL buffer specified by
  \CArg{mode}.  This buffer is also used to write back fully composited
  images if the \CEnum{ICET\_GL\_DISPLAY} option is on.

  \CArg{mode} is an \OpenGL value that specifies the buffer.  It is passed
  to \CFuncExternal{glReadBuffer} and \CFuncExternal{glDrawBuffer}.
  Accepted values are \CEnum{GL\_FRONT}, \CEnum{GL\_BACK},
  \CEnum{GL\_LEFT}, \CEnum{GL\_RIGHT}, \CEnum{GL\_FRONT\_LEFT},
  \CEnum{GL\_FRONT\_RIGHT}, \CEnum{GL\_BACK\_LEFT},
  \CEnum{GL\_BACK\_RIGHT}, and any of the \CEnum{GL\_AUX}\emph{i}
  identifiers.

  The current read buffer used is stored in the
  \CEnum{ICET\_GL\_READ\_BUFFER} state variable.  The default value is
  \CEnum{GL\_BACK}.


  \mansection{Errors}

  \begin{Description}[ICET\_INVALID\_OPERATION]
  \item[\CErrorEnum{ICET\_INVALID\_OPERATION}]
    \CFunc{icetGLInitialize} has not been called for this \IceT context.
  \item[\CErrorEnum{ICET\_INVALID\_ENUM}]
    \CArg{mode} is not a known \OpenGL buffer identifier.
  \end{Description}


  \mansection{Warnings}

  None.


  \mansection{Bugs}

  The check of \CArg{mode} is perfunctory.  It just checks \CArg{mode}
  against a list of known buffers.  It does not check to see if the buffer
  actually exists or for any other buffers that might be defined in an
  \OpenGL extension.


  \mansection{Copyright}
  Copyright \copyright 2010 Sandia Corporation

  Under the terms of Contract DE-AC04-94AL85000, there is a non-exclusive
  license for use of this work by or on behalf of the U.S. Government.
  Redistribution and use in source and binary forms, with or without
  modification, are permitted provided that this Notice and any statement
  of authorship are reproduced on all copies.


  \mansection{See Also}

  \CFuncSeeAlso{icetGLDrawCallback}

\end{Name}


% These are emacs settings that go at the end of the file.
% Local Variables:
% writestamp-format: "%B %e, %Y"
% writestamp-prefix: "^\\\\setDate{"
% writestamp-suffix: "}$"
% End:
