% -*- latex -*-

  \begin{Description}
  \item[\CEnum{ICET\_STRATEGY\_SEQUENTIAL}]
    Basically applies a ``traditional'' single tile composition (such as
    binary swap) to each tile in the order they were defined.  Because each
    process must take part in the composition of each tile regardless of
    whether they draw into it, this strategy is usually inefficient
    when compositing for more than one tile, but is fine for the single
    tile case.
    \index{strategy!sequential}
  \item[\CEnum{ICET\_STRATEGY\_DIRECT}] As each process renders an image
    for a tile, that image is sent directly to the process that will
    display that tile.  This usually results in a few processes receiving
    and processing the majority of the data, and is therefore usually an
    inefficient strategy.
    \index{strategy!direct}
  \item[\CEnum{ICET\_STRATEGY\_SPLIT}] Like \CEnum{ICET\_STRATEGY\_DIRECT},
    except that the tiles are split up, and each process is assigned a
    piece of a tile in such a way that each process receives and handles
    about the same amount of data.  This strategy is often very efficient,
    but due to the large amount of messages passed, it has not proven to be
    very scalable or robust.
    \index{strategy!split}
  \item[\CEnum{ICET\_STRATEGY\_REDUCE}] A two phase algorithm.  In the
    first phase, tile images are redistributed such that each process has
    one image for one tile.  In the second phase, a ``traditional'' single
    tile composition is performed for each tile.  Since each process
    contains an image for only one tile, all these compositions may happen
    simultaneously.  This is a well rounded strategy that seems to perform
    well in a wide variety of applications.
    \index{strategy!reduce}
  \item[\CEnum{ICET\_STRATEGY\_VTREE}] An extension to the binary tree
    algorithm for image composition.  Sets up a ``virtual'' composition
    tree for each tile image.  Processes that belong to multiple trees
    (because they render to more than one tile) are allowed to float
    between trees.  This strategy is not quite as well load balanced as
    \CEnum{ICET\_STRATEGY\_REDUCE} or \CEnum{ICET\_STRATEGY\_SPLIT}, but
    has very well behaved network communication.
    \index{strategy!virtual~trees}
  \end{Description}
